\chapter*{Preface}

This is a P7 project written at the Department of Mathematical Sciences at Aalborg University.
As such it is expected to have the general knowledge acquired during a bachelors degree in mathematics. In addition it is expected that the reader is familiar with the following:
\begin{enumerate}
  \item The basics algebraic geometry, in particular the theory of protective regular and absolutely irreducible curves over $\mathbb{F}_q$
  \item The basics of error correcting codes.
  \item The basic construction and properties of algebraic geometry codes.
\end{enumerate}


The work on the project took place from the 1. of September to the 20. of December 2023.

Sources are stated at the start of each chapter, or section if the sources used in the section differ from the sources, that are generally used within the chapter.

Definitions, algorithms, theorems, propositions, lemmas, corollaries, examples, and remarks are numbered according to each chapter and consecutively.
Equations are also numbered according to each chapter but separately. % and likewise with figures and tables.
The conclusions of proofs and examples are marked with $\blacksquare$ and $\square$ respectively.

A table of notation and shorthands is given after the list of contents.
Please note that some symbols may be used differently in different chapters.

%Finally, I wish to thank and acknowledge my supervisor Matteo Bonini for his guidance and for being indulgent enough, to answer questions with no imitate application to the project.

\vspace{\baselineskip}\hfill Aalborg University, \today
\vfill\noindent

\begin{minipage}[H]{\textwidth}
 \centering
 \rule{\textwidth / 2}{1pt}\\
  Martin Sig Nørbjerg\\
 {\footnotesize mnarbj20@student.aau.dk}
\end{minipage}
\hfill
